%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
%
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\usepackage{color}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{array}
\usepackage{url}

\newcommand{\note}[1]{\textcolor{red}{\textbf{#1}}}

\title{\LARGE \bf
Proctor: Evaluating 3-D Recognition
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Warren He, Sergey Karayev, Trevor Darrell, Radu Rusu, Pieter
  Abbeel}

%\author{Some people% <-this % stops a space
%\thanks{This work was not supported by any organization}% <-this % stops a space
%\thanks{H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
%        University of Twente, 7500 AE Enschede, The Netherlands
%        {\tt\small h.kwakernaak@autsubmit.com}}%
%\thanks{P. Misra is with the Department of Electrical Engineering, Wright State University,
%        Dayton, OH 45435, USA
%        {\tt\small pmisra@cs.wright.edu}}%
%}


\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}


Until recently, the field of 3D perception was a niche domain. With the advent
of inexpensive and accurate 3D imaging sensors, there has been an explosion of
interest in 3D point clouds across a broad range of researchers and application
developers. In the past few years, various research fields have developed
many different feature representations that operate in 3D geometry spaces, but
no unified evaluation has ever been performed due to a poor intersection between
these burgeoning communities.

In this paper we present a comprehensive evaluation framework for 3D point
cloud-based recognition: Proctor.
The framework is designed to automatically test large ranges of
parameters and estimate several metrics that can be automatically included in
future publications. To encourage its use, we release the entire Proctor
infrastructure under a permissive BSD license, linked to the Point Cloud
Library (PCL) project~\cite{PCL}.

%Recently proliferation of cheap 3-D sensors.
%Lots of work on feature representations.
%But no unified evaluation available.
%We present an evaluation framework for point cloud-based recognition.
%Flexible as to dataset and feature.
%Modular design.
%Provides several metrics.
%Open source.

We believe that the proposed standard evaluation framework will boost
research progress in this field.

\end{abstract}

\input{intro_and_related_work.tex}

\input{architecture.tex}

\input{evaluation.tex}

\section{COMMUNITY AND FUTURE PLANS}

This paper describes the motivation for a standard 3-D recognition pipeline
evaluation framework and explains our choices for the particular components of
our implementation.

We hope that future work in 3-D feature detection, description, or subsequent
recognition or pose estimation mechanisms will base itself on this framework.
The project of a general, modular 3-D preception evaluation framework is
tremendous, and would benefit from code and testing contributions as much as its
existence benefits researchers in these areas.

Therefore we have provided all code and documentation under a permissive BSD
open-source license, and welcome future
contributions at \url{http://www.pointclouds.org/proctor}.

Our future work includes the expansion of feature descriptors to be tested,
including texture descriptors that operate on RGBD-like datasets, as well as
more comprehensive detection/evaluation mechanisms for ``global'' descriptors.

% \note{more about next steps?}

% \section{ACKNOWLEDGMENTS}
% 
% The authors gratefully acknowledge the contribution of National Research Organization and reviewers' comments.

{\small
\bibliographystyle{ieee}
\bibliography{sergeyk-icra12,misc}
}

\end{document}
